\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@

%%%%%%%%%%%%%
\subsection{Capturing Flow Dynamics and Fingering Growth with Adaptive Mesh Resolution}\label{section:results_hete_fix_adapt}    
%\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
In most numerical simulations involving geofluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features. Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces. This leads to mesh grid that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.

>>>>

\red{(KOSTAS: YOU HAVE REMOVED 1 SIMULATION HERE ... THEREFORE YOU NEED TO MAKE SURE THAT THE TEXT REFLECT THE NEW FIGURE'S CONFIGURATION!!)}

@@

%%%%%%%%%%%%%
\subsection{Capturing Flow Dynamics and Fingering Growth: Impact of Mesh Resolution}\label{section:results_hete_fix_adapt}    
%\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
In most numerical simulations involving geofluid dynamics local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features. Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces. This leads to mesh grid that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.

In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the nucleation of fingers was demonstrated in homogeneous porous media
